Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-08 modeling-volunteer-computing-gecco.tex
Changes to the results section

The initial code was only modified to represent the fitness in a chart
(that uses the {\tt chart.js} JavaScript library) so that the user has
a visual feedback of what is going on. The {\em migration} part is
also added: after every 100 generations, a single individual is sent
to the server and another request is made to the server of a single
and random individual; this algorithm can be also run locally, the
algorithm does not stop if there is no answer from the server. As a
summary, the only thing needed to run an evolutionary algorithm in the browser is to add {\em migration} functions to the original one.

@@

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the
experiment, the ordinal number of the experiment that is being performed or the content of the chromosome pool, and code to serve the static pages
and the JavaScript/CSS
code also. The main changes to the code from the  the previous paper
\cite{arxiv:modeling} is, besides the inclusion of logging for a
better experiment analyis, the function that checks for the algorithm
termination condition and restarts the chromosome pool when
it does; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version. %FERGU: es esta la única innovación al paper de Arxiv? A lo mejor no deberíamos mencionarlo ni usarlo como base

All in all, it amounts to a few hundred lines of code
including all languages (client and server JavaScript, HTML and CSS). This code can
be deployed, in principle, in any server that is able to run node.js.

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}, and they 
will be analyzed in the next section.

>>>>

@@

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the
experiment, the ordinal number of the experiment that is being performed or the content of the chromosome pool, and code to serve the static pages
and the JavaScript/CSS
code also. The main changes to the code from the  the previous paper
\cite{arxiv:modeling} is, besides the inclusion of logging for a
better experiment analyis, the function that checks for the algorithm
termination condition and restarts the chromosome pool when
it does; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version. %FERGU: es esta la única innovación al paper de
                  %Arxiv? A lo mejor no deberíamos mencionarlo ni
                  %usarlo como base
% La principal innovación es que es más fácil recoger datos del
% servidor y que el despliegue es automático - JJ

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://git.io/nodio}, and they 
will be analyzed in the next section.
